Boilerplate logger: A logger for developers by developers

### 2020-04-10 paper/paper.tex
[paper] Draft1.1 from review comments
Incorporate review comments from friends.

\title{Boilerplate logging: Logs for developers by developers}
\subtitle{Homework 5}
\author{Evan Lee}
\affiliation{%
    \institution{University of Colorado Boulder}
    \city{Boulder}
    \state{Colorado}
}
\email{evan.n.lee@colorado.edu}
\date{April 2020}

@@

    % Why is the problem hard?
    To reiterate: the cost of managing this balancing act is hidden at best and outright obscured at worst. On an individual basis, even considering changes to code that have to do with so-called boilerplate logging may incur a small, nearly insignificant cost but these small costs add up over the span of the industry and especially over the span of time. In addition, logging at its heart is a subjective activity. Different developers from different backgrounds using different languages with different frameworks all will use unique styles of logging and make unique decisions on log positions, formatting, substance, and level. This presents difficulty in the qualitative analysis of boilerplate logging broadly and generally throws a wrench into any standardization activity.

@@

    In addition, consider the additional benefit that boilerplate logging provides in the above example. Take a situation where a future maintainer of the code must also capture the \lstinline{header} object being provided to the \lstinline{post} method in the logs for any reason; now an additional iteration of code must be developed and committed.

>>>>

\title{Boilerplate logger: A logger for developers by developers}
\subtitle{Homework 5}
\author{Evan Lee}
\affiliation{%
    \institution{University of Colorado Boulder}
    \city{Boulder}
    \state{Colorado}
}
\email{evan.n.lee@colorado.edu}
\date{April 2020}

@@

    % Why is the problem hard?
    To reiterate: the cost of managing this balancing act is hidden at best and outright obscured at worst. Developers even considering changes that have to do with logging incur a small, nearly insignificant cost. These small costs add up over the span of the industry and especially over the span of time. In addition, logging at its heart is a subjective activity. Different developers from different backgrounds using different languages with different frameworks all will use unique styles of logging and make unique decisions on log positions, formatting, substance, and level. This presents difficulty in the qualitative analysis of logging and generally throws a wrench into any standardization activity.

@@

    In addition, consider the additional benefit that boilerplate logging provides in the above example. Take a situation where a future maintainer of the code must also capture the \lstinline{header} object being provided to the \lstinline{post} method in the logs for any reason -- now an additional iteration of code must be developed and committed.
